---
title: "Sandbox"
output: github_document
---

# Information

Author: Matthew T. Warketin 
Email: <warkentin@lunenfeld.ca>

This is some text to describe my sandbox repo. This repo contains my dev code
for miscellaneous functions that I write in R and have documented as a R package.

Here is some of the important functions in this package:

- IndexOfUnion
- That's it


## Index of Union

Here is some text to describe the `IndexOfUnion` function.

```{r, echo=FALSE}
data("iris")
iris$new <- ifelse(iris$Species=='setosa', 1, 0)
```

We have loaded the data so lets fit a ROC using `pROC`s function called `roc`.

```{r, warning=FALSE, message=FALSE}
library(pROC)
model <- glm(new ~ Sepal.Width, data = iris, family = 'binomial')
iris$pred <- predict(model, newdata = iris, type = 'response')
(rocauc <- roc(iris$new, iris$pred))
```

The AUC for this logistic regression model is `r round(rocauc$auc, 2)`.

Now to run `IndexOfUnion` function...

Here is an important concept [^1]

```{r}
library(sandbox)
?indexOfUnion
```

[^1]: Important citation
