---
title: "Best ROC Threshold"
author: "Matthew T. Warkentin"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

Vignettes are long form documentation commonly included in packages. Because they are part of the distribution of the package, they need to be as compact as possible. The `html_vignette` output type provides a custom style sheet (and tweaks some options) to ensure that the resulting html is as small as possible. The `html_vignette` format:

- Never uses retina figures
- Has a smaller default figure size
- Uses a custom CSS stylesheet instead of the default Twitter Bootstrap style

## Index of Union

Here is some text to describe the `IndexOfUnion` function.

```{r, echo=FALSE}
data("iris")
iris$new <- ifelse(iris$Species=='setosa', 1, 0)
```

We have loaded the data so lets fit a ROC using `pROC`s function called `roc`.

```{r, warning=FALSE, message=FALSE}
library(pROC)
model <- glm(new ~ Sepal.Width, data = iris, family = 'binomial')
iris$pred <- predict(model, newdata = iris, type = 'response')
(rocauc <- roc(iris$new, iris$pred))
```

The AUC for this logistic regression model is `r round(rocauc$auc, 2)`.

Now to run `IndexOfUnion` function...

Here is an important concept [^1]

```{r}
library(sandbox)
?indexOfUnion
```

[^1]: Important citation
